%
%  untitled
%
%  Created by Alexis on 2012-11-04.
%  Copyright (c) 2012 . All rights reserved.
%
\documentclass[]{article}

% Use utf-8 encoding for foreign characters
\usepackage[utf8]{inputenc}

% Setup for fullpage use
\usepackage{fullpage}

% Uncomment some of the following if you use the features
%
% Running Headers and footers
%\usepackage{fancyhdr}

% Multipart figures
%\usepackage{subfigure}

% More symbols
%\usepackage{amsmath}
%\usepackage{amssymb}
%\usepackage{latexsym}

% Surround parts of graphics with box
\usepackage{boxedminipage}

% Package for including code in the document
\usepackage{listings}

% If you want to generate a toc for each chapter (use with book)
\usepackage{minitoc}

% This is now the recommended way for checking for PDFLaTeX:
\usepackage{ifpdf}

%\newif\ifpdf
%\ifx\pdfoutput\undefined
%\pdffalse % we are not running PDFLaTeX
%\else
%\pdfoutput=1 % we are running PDFLaTeX
%\pdftrue
%\fi

\ifpdf
\usepackage[pdftex]{graphicx}
\else
\usepackage{graphicx}
\fi
\title{CS760 \\ Project Proposal}
\author{  Alexis Fisher }

%\date{2012-11-04}

\begin{document}

\ifpdf
\DeclareGraphicsExtensions{.pdf, .jpg, .tif}
\else
\DeclareGraphicsExtensions{.eps, .jpg}
\fi

\maketitle


%\begin{abstract}
%\end{abstract}

\section{Goal}
Implement a 5-card draw poker player that outperforms a random player. Initial implementation assumes two players (the learned player and another player, either random, a person, or another learned player). 

\section{Implementation}
To create a 5-card draw poker player implemented via a reinforcement-learning approach.  The constructed Player will retain memory of its initial and current hand to decide which cards to forfeit during the draw. To learn the Q algorithm, the reward signal is the ranking of the player's current poker hand, and the actions available are drawing [0-3] cards. I plan to implement this in Python.

\section{Experiments}
To gain an understanding and evidence of performance, I plan to measure performance against a random player and the Bayesian Poker Player from Monash University~\cite{korb99}. Performance is based on win/loss of a hand, averaged over thousands of hands.  

\section{Data Set}
The UCI poker hands data set~\cite{pokerdata} will be used. This data set includes ranked ``Poker Hand'' information, which will assist in determining the reward signal. 

\bibliographystyle{plain}
%\bibliography{}
\begin{thebibliography}{9}
\bibitem{korb99}
K.B. Korb, A.E. Nicholson and N. Jitnah,
 \emph{Bayesian Poker}. 
In Proc. of Uncertainty in Artificial Intelligence, pp. 343-350, 
Stockholm, Sweden, August, 1999.

\bibitem{pokerdata}
\emph{Poker Hand Data Set}
http://archive.ics.uci.edu/ml/datasets/Poker+Hand
\end{thebibliography}
\end{document}
